\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
I would like to thank my supervisor, Marek Kowalski, for extending me the opportunity to become part of the excellent Neutrino Astronomy group at DESY. Thank you for being both a critical and extremely helpful mentor, and for creating a warm, happy, and fun environment for everyone working at DESY.

I would also like to express my deepest gratitude to Markus Ackermann for advising me throughout the work on this thesis. Thank you for the discussions whenever I needed them, for stepping in each time it felt like a dead end, and for being patient with me, allowing me to work at the pace I was most comfortable with.

A very big thanks to Jakob Van Santen for co-supervising this thesis and for all your fun anecdotes along the way. Thank you for knowing almost everything about simulations and reconstruction, and for selflessly helping me understand these concepts every time I knocked on your door. Thank you for making me believe in myself and my work with your constant encouragement for even my smallest accomplishments! I would also like to thank Summer Blot for many informal discussions about ice models and detectors, as well as for your constant support in every social aspect of a PhD student's life.

To my colleagues at DESY, including but not limited to Zack, Leander, RJ, Pavlo, Jonas, Navid, and Teresa, thank you for making this the most amazing chapter of my life. We supported each other through what might have been the worst time for everyone—the COVID-19 pandemic. Starting my PhD during this period would have been impossible without you all. Thank you for the parties, trips, jokes, and games—it was wonderful. Thank you for everything I have learned from you all, whether scientific, social, or cultural. A special thanks to Jannis for starting and finishing the thesis writing process alongside me, and for the constant check-ins that kept me motivated throughout.

A big thanks to Richard for being there from the beginning to the end of this journey, for every step of the analysis and my time in Berlin. Thank you for helping me with complex software and simulations, for laying the groundwork, and for our countless discussions about statistical methods and whiteboard explanations!

Thank you to Cristina, Sofia, and Nora for becoming not just office colleagues but my closest friends. For all the girls' nights where you allowed me to showcase my cooking and bartending skills, for sharing my interests, and for understanding all the visa, contract, and work-related problems I faced. Thank you for always being there for me and for never letting me miss my family.

I'd also like to thank the IceCube Collaboration for letting me work with their data. I'd like to thank colleagues from the collaboration—Erik, Phillip, and Jakob—for your expertise on SnowStorm and NNMFit. Thank you for helping solve the most trivial issues we faced. A special thanks to Aswathi, Vedant, and Rogan for making my time in Madison enjoyable. I'd also like to thank Juliana Stachurska for letting me take over your work and for constantly helping me, even while managing your own projects.

I am also immensely grateful to my friends in India—Soumi, Pratik, and Renuka—for your constant support, your many long phone calls, and your friendship through every challenge, especially during the pandemic.

To my family— Mummy, Papa, my sisters Didi and Hetal, my nephew Mehan, and many others—your unwavering support and encouragement have brought me to this point. I owe this work to you; thank you for believing in me and for loving me unconditionally, supporting every aspect and decision in my life.

Last but not least, Raffael, thank you for being at DESY so that our paths could cross. Thank you for standing by me in every phase, whether joyful or challenging. 