\thispagestyle{plain}
\begin{center}
	\vspace*{1cm}

	\LARGE
	\textbf{First Search for Heavy Neutral Leptons with IceCube DeepCore}
	\large

	\vspace{0.8cm}

	\textbf{Dissertation}\\
	zur Erlangung des akademischen Grades\\
	doctor rerum naturalium \\
	(Dr. rer. nat.) \\

	\vspace{0.5cm}

	im Fach: Physik \\
	Spezialisierung: Experimentalphysik\\

	\vspace{0.5cm}

	eingereicht an der \\
	Mathematisch-Naturwissenschaftlichen Fakultät\\
	der Humboldt-Universität zu Berlin\\

	\vspace{0.5cm}

	von\\
	\textbf{Leander Fischer M. Sc.}\\
	%	\vspace{0.8cm}
	geboren am 24. Oktober 1992\\
	in Heidelberg

	\vspace{0.5cm}

	Präsidentin der Humboldt-Universität zu Berlin \\
	Prof. Dr. Julia von Blumenthal \\

	\vspace{0.5cm}

	Dekanin der Mathematisch-Naturwissenschaftlichen Fakultät \\
	Prof. Dr. Caren Tischendorf \\

	\vspace{0.5cm}

	% % uncomment for publication
	% Gutachter:innen:
	% Prof. Dr. Marek Kowalski, Humboldt-Universität zu Berlin \\
	% Prof. Dr. Joachim Kopp, Johannes Gutenberg-Universität Mainz \\
	% Dr. Priscilla Pani, DESY Zeuthen \\

	% \vspace{0.5cm}

	% Tag der mündlichen Prüfung: xx.xx.2024

\end{center}

\newpage
\thispagestyle{plain}

\begin{flushleft}	
	\vspace*{8cm}
	
	\textbf{Copyright Notice} \\
	This book is released into the public domain using the CC-BY-4.0 code.

	To view a copy of the CC-BY-4.0 code, visit: \\\url{https://creativecommons.org/licenses/by/4.0/}

	\medskip
	
	\textbf{Colophon} \\
	This document was typeset with the help of \href{https://sourceforge.net/projects/koma-script/}{\KOMAScript} and \href{https://www.latex-project.org/}{\LaTeX} using the open-source \href{https://github.com/fmarotta/kaobook/}{kaobook} template class. \\
	
	\medskip
	
	The source code of this thesis is available  at: \\\url{https://github.com/LeanderFischer/phd_thesis}

	\medskip

	% \textbf{Publisher} \\
	% First printed in Nov 2022 by Humboldt Universität zu Berlin
	% \todo[inline, noinlinepar]{add when first printed and by whom}
\end{flushleft}
	

% \newpage
% \thispagestyle{plain}

% \vspace*{5.0cm}

% \large
% \noindent A neutrino is not a big thing to be hit by. In fact it's hard to think of anything much smaller by which one could reasonably hope to be hit. And it's not as if being hit by neutrinos was in itself a particularly unusual event for something the size of the Earth. Far from it. It would be an unusual nanosecond in which the Earth was not hit by several billion passing neutrinos.\\

% \flushright --\textit{The Hitchhiker's Guide to The Galaxy}